Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] last changes.

\begin{align}
  \label{eq:uh-definition}
    &\fuh_{0} &&: \Prop → \Prop\\
    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
    &\fuh_{0}\ φ &&= φ
\end{align}

@@

\begin{table}[!ht]
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
    \texttt{canonicalize}
      &Normalization of the formula
      &Thm.~\ref{thm:canonicalizeThm}
    \\
    \texttt{clausify}
      &Performs clausification
      &Thm.~\ref{thm:clausifyThm}
    \\
    \hyperlink{atp-conjunct}{\texttt{conjunct}}
      &Takes a formula from a conjunction
      &Thm.~\ref{thm:conjunctThm}
    \\
    \texttt{negate}
      &Negate the formula
      &Thm.~\ref{thm:negateThm}
    \\
    \texttt{resolve}
      &A general form of the resolution theorem
      &Thm.~\ref{thm:resolveThm}
    \\
    \texttt{simplify}
      &Simplify definitions and theorems
      &Thm.~\ref{thm:simplifyThm}
    \\
    \texttt{strip}
      &Strip a goal into subgoals
      &Thm.~\ref{thm:stripThm}
    \\[1ex]
    \hline
    \end{tabular}}
  \end{center}
\label{tab:agda-metis-table}
\end{table}
% ------------------------------------------------------------------------------

\subfile{sections/proof-reconstruction/strip.tex}
\subfile{sections/proof-reconstruction/negate.tex}
\subfile{sections/proof-reconstruction/resolve.tex}
\subfile{sections/proof-reconstruction/canonicalize.tex}
\subfile{sections/proof-reconstruction/conjunct.tex}
\subfile{sections/proof-reconstruction/clausify.tex}
\subfile{sections/proof-reconstruction/simplify.tex}

% ------------------------------------------------------------------------------

>>>>

% \begin{functiondef}{$\fuh_{0}$ : \Prop → \Prop}
%   \label{eq:uh-definition}

% \begin{array}
%     &\fuh_{0} &&: \Prop → \Prop\\
%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
%     &\fuh_{0}\ φ &&= φ
% \end{array}

% \end{functiondef}

@@

\begin{table}[!ht]
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
    \texttt{canonicalize}
      &Normalization of the formula
      &Thm.~\ref{thm:canonicalize}
    \\
    \texttt{clausify}
      &Performs clausification
      &Thm.~\ref{thm:clausify}
    \\
    \hyperlink{atp-conjunct}{\texttt{conjunct}}
      &Takes a formula from a conjunction
      &Thm.~\ref{thm:conjunct}
    \\
    \texttt{negate}
      &Negate the formula
      &Thm.~\ref{thm:negate}
    \\
    \texttt{resolve}
      &A general form of the resolution theorem
      &Thm.~\ref{thm:resolve}
    \\
    \texttt{simplify}
      &Simplify definitions and theorems
      &Thm.~\ref{thm:simplify}
    \\
    \texttt{strip}
      &Strip a goal into subgoals
      &Thm.~\ref{thm:strip}
    \\[1ex]
    \hline
    \end{tabular}}
  \end{center}
\label{tab:agda-metis-table}
\end{table}

% -----------------------------------------------------------------------------

\subfile{sections/proof-reconstruction/strip.tex}
% \subfile{sections/proof-reconstruction/negate.tex}
% \subfile{sections/proof-reconstruction/resolve.tex}
% \subfile{sections/proof-reconstruction/canonicalize.tex}
% \subfile{sections/proof-reconstruction/conjunct.tex}
% \subfile{sections/proof-reconstruction/clausify.tex}
% \subfile{sections/proof-reconstruction/simplify.tex}

%------------------------------------------------------------------------------
